\documentclass[DM,lsstdraft,STR,toc]{lsstdoc}
\usepackage{geometry}
\usepackage{longtable,booktabs}
\usepackage{enumitem}
\usepackage{arydshln}
\usepackage{attachfile}
\usepackage{array}

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{#1}}

\input meta.tex

\newcommand{\attachmentsUrl}{https://github.com/\gitorg/\lsstDocType-\lsstDocNum/blob/\gitref/attachments}
\providecommand{\tightlist}{
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\setcounter{tocdepth}{4}

\begin{document}

\def\milestoneName{Large Scale Data Access CCOB data}
\def\milestoneId{LDM-503-10b}
\def\product{DBB Services}

\setDocCompact{true}

\title{LDM-503-10b: Large Scale CCOB Data Access Test Plan and Report}
\setDocRef{\lsstDocType-\lsstDocNum}
\date{\vcsdate}
\author{ Michelle Butler }

\input{history_and_info.tex}


\setDocAbstract{
This is the test plan and report for LDM-503-10b (Large Scale Data Access CCOB data),
an LSST milestone pertaining to the Data Management Subsystem.
}


\maketitle

\section{Introduction}
\label{sect:intro}


\subsection{Objectives}
\label{sect:objectives}

 Demonstrate the ability to transfer data from the CCOB or SLAC with 21
rafts ~of data and ingest at LDF and make available through an instance
of the LSP. ~This is a data transfer of data from SLAC or some other
site with 21-raft-sized images to NCSA, ingest it into a Butler
environment and place the file into file systems readable by the LSP.
The CCOB device might NOT be available, but as 21 raft size data will be
available from a test stand at SLAC, we will use a generic test stand
data transfer method (e.g., rsync) to bring designated data to NCSA,
ingest it, and place into appropriate filesystems, and make available
through the LSP.



\subsection{System Overview}
\label{sect:systemoverview}

 This milestone is for bringing data from a test stand at SLAC that
contains the test data for 21 rafts single image data with proper
headers. ~ ~That data is to be transferred to the LDF and ingested into
the Butler, and then placed in file systems that are viewable by the
LSP. ~\\[2\baselineskip]

\subsection{Applicable Documents}\label{applicable-documents}

\citeds{LDM-294} Data Management Organization and Management\\
\citeds{LDM-503} DM Test Plan\\
\citeds{LDM-148} Data Management System Design


\subsection{Document Overview}
\label{sect:docoverview}

This document was generated from Jira, obtaining the relevant information from the
\href{https://jira.lsstcorp.org/secure/Tests.jspa\#/testPlan/LVV-P55}{LVV-P55}
~Jira Test Plan and related Test Cycles (
\href{https://jira.lsstcorp.org/secure/Tests.jspa\#/testCycle/LVV-C108}{LVV-C108}
).

Section \ref{sect:intro} provides an overview of the test campaign, the system under test (\product{}),
the applicable documentation, and explains how this document is organized.
Section \ref{sect:testplan} provides additional information about the test plan, like for example the configuration
used for this test or related documentation.
Section \ref{sect:personnel} describes the necessary roles and lists the individuals assigned to them.

Section \ref{sect:overview} provides a summary of the test results, including an overview in Table \ref{table:summary},
an overall assessment statement and suggestions for possible improvements.
Section \ref{sect:detailedtestresults} provides detailed results for each step in each test case.

The current status of test plan \href{https://jira.lsstcorp.org/secure/Tests.jspa\#/testPlan/LVV-P55}{LVV-P55} in Jira is \textbf{ Approved }.

\subsection{References}
\label{sect:references}
\renewcommand{\refname}{}
\bibliography{lsst,refs,books,refs_ads,local}


\newpage
\section{Test Plan Details}
\label{sect:testplan}


\subsection{Data Collection}

  Observing is not required for this test campaign.

\subsection{Verification Environment}
\label{sect:hwconf}
  21 raft scale data created from a test stand at SLAC, data transfer
environment installed somewhere at SLAC, data transfer environment
installed at NCSA, and LSP installed at NCSA/LDF~

  \subsection{Entry Criteria}
  Data available for viewing with proper headers.~~

  \subsection{Exit Criteria}
  Data is viewable on LSP.~~


\subsection{Related Documentation}

The documentation related to this test campaign should be provided in the following DocuShare Collection
(as per Verification Artifacts in Jira test plan LVV-P55).

\begin{itemize}
\item DocuShare Collection Not Specified
\end{itemize}



\subsection{PMCS Activity}

Primavera milestones related to the test campaign.

\begin{itemize}
\item None
\end{itemize}


\newpage
\section{Personnel}
\label{sect:personnel}

The personnel involved in the test campaign is shown in the following table.

{\small
\begin{longtable}{p{3cm}p{3cm}p{3cm}p{6cm}}
\hline
\multicolumn{2}{r}{T. Plan \href{https://jira.lsstcorp.org/secure/Tests.jspa\#/testPlan/LVV-P55}{LVV-P55} owner:} &
\multicolumn{2}{l}{\textbf{ Michelle Butler } }\\\hline
\multicolumn{2}{r}{T. Cycle \href{https://jira.lsstcorp.org/secure/Tests.jspa\#/testCycle/LVV-C108}{LVV-C108} owner:} &
\multicolumn{2}{l}{\textbf{
Michelle Butler }
} \\\hline
\textbf{Test Cases} & \textbf{Assigned to} & \textbf{Executed by} & \textbf{Additional Test Personnel} \\ \hline
\href{https://jira.lsstcorp.org/secure/Tests.jspa#/testCase/LVV-T1556}{LVV-T1556}
& {\small Michelle Butler } & {\small  } &
\begin{minipage}[]{6cm}
\smallskip
{\small  }
\medskip
\end{minipage}
\\ \hline
\end{longtable}
}

\newpage

\section{Test Campaign Overview}
\label{sect:overview}

\subsection{Summary}
\label{sect:summarytable}

{\small
\begin{longtable}{p{2cm}cp{2.3cm}p{8.6cm}p{2.3cm}}
\toprule
\multicolumn{2}{r}{ T. Plan \href{https://jira.lsstcorp.org/secure/Tests.jspa\#/testPlan/LVV-P55}{LVV-P55}:} &
\multicolumn{2}{p{10.9cm}}{\textbf{ LDM-503-10b: Large Scale Data Access CCOB data }} & Approved \\\hline
\multicolumn{2}{r}{ T. Cycle \href{https://jira.lsstcorp.org/secure/Tests.jspa\#/testCycle/LVV-C108}{LVV-C108}:} &
\multicolumn{2}{p{10.9cm}}{\textbf{ LDM-503-10b Large Scale CCOB Data Access }} & Not Executed \\\hline
\textbf{Test Cases} &  \textbf{Ver.} & \textbf{Status} & \textbf{Comment} & \textbf{Issues} \\\toprule
\href{https://jira.lsstcorp.org/secure/Tests.jspa#/testCase/LVV-T1556}{LVV-T1556}
&  1
& Not Executed &
\begin{minipage}[]{9cm}
\smallskip

\medskip
\end{minipage}
&
\\\hline
\caption{Test Campaign Summary}
\label{table:summary}
\end{longtable}
}

\subsection{Overall Assessment}
\label{sect:overallassessment}

Not yet available.

\subsection{Recommended Improvements}
\label{sect:recommendations}

Not yet available.

\newpage
\section{Detailed Test Results}
\label{sect:detailedtestresults}

\subsection{Test Cycle LVV-C108 }

Open test cycle {\it \href{https://jira.lsstcorp.org/secure/Tests.jspa#/testrun/LVV-C108}{LDM-503-10b Large Scale CCOB Data Access}} in Jira.

Test Cycle name: LDM-503-10b Large Scale CCOB Data Access\\
Status: Not Executed

Demonstrate the ability to transfer data from the CCOB with 21 rafts
from SLAC and ingested at NCSA and make available through an instance of
the LSP\\[2\baselineskip]

\subsubsection{Software Version/Baseline}
Not provided.

\subsubsection{Configuration}
21 Raft data with proper headers at SLAC. ~ Data transfer environment
installed on SLAC systems. ~Data transfer environment at NCSA. ~Ingest
software installed at LDF. ~LSP environment installed at NCSA.~~

\subsubsection{Test Cases in LVV-C108 Test Cycle}

\paragraph{ LVV-T1556 - LDM-503-10B Large Scale CCOB Data Access }\mbox{}\\

Version \textbf{1}.
Open  \href{https://jira.lsstcorp.org/secure/Tests.jspa#/testCase/LVV-T1556}{\textit{ LVV-T1556 } }
test case in Jira.

Demonstrate the ability to transfer data from the SLAC test stand or
CCOB with 21 rafts from SLAC and ingested at NCSA and make available
through an instance of the LSP

\textbf{ Preconditions}:\\
SLAC or some other test stand needs to have produced 21 rafts of data
that has some enviornment for transferring the data to NCSA.~ ~

Execution status: {\bf Not Executed }

Final comment:\\


Detailed steps results:

\begin{longtable}{p{1cm}p{15cm}}
\hline
{Step} & Step Details\\ \hline
1 & Description \\
 & \begin{minipage}[t]{15cm}
{\footnotesize
Have a system at SLAC that has the 21 raft data that needs to be
transferred to NCSA, and all accounts and scripts installed on
environment that can read that data.~ ~

\medskip }
\end{minipage}
\\ \cdashline{2-2}

 & Test Data \\
 & \begin{minipage}[t]{15cm}{\footnotesize
21 rafts of data with proper headers~

\medskip }
\end{minipage} \\ \cdashline{2-2}

 & Expected Result \\
 & \begin{minipage}[t]{15cm}{\footnotesize
scripts are able to transfer the data to NCSA though rsync or bbcp.
~\\[2\baselineskip]

\medskip }
\end{minipage} \\ \cdashline{2-2}

 & Actual Result \\
 & \begin{minipage}[t]{15cm}{\footnotesize

\medskip }
\end{minipage} \\ \cdashline{2-2}

 & Status: \textbf{ Not Executed } \\ \hline

2 & Description \\
 & \begin{minipage}[t]{15cm}
{\footnotesize
Data is transferred to NCSA and ingested into Butler~

\medskip }
\end{minipage}
\\ \cdashline{2-2}

 & Test Data \\
 & \begin{minipage}[t]{15cm}{\footnotesize
21 rafts of data~

\medskip }
\end{minipage} \\ \cdashline{2-2}

 & Expected Result \\
 & \begin{minipage}[t]{15cm}{\footnotesize
Data is transferred to NCSA, and can now be see in file systems by the
LSP. ~\\[2\baselineskip]

\medskip }
\end{minipage} \\ \cdashline{2-2}

 & Actual Result \\
 & \begin{minipage}[t]{15cm}{\footnotesize

\medskip }
\end{minipage} \\ \cdashline{2-2}

 & Status: \textbf{ Not Executed } \\ \hline

3 & Description \\
 & \begin{minipage}[t]{15cm}
{\footnotesize
using the LSP view the data in the ingested directory~

\medskip }
\end{minipage}
\\ \cdashline{2-2}

 & Test Data \\
 & \begin{minipage}[t]{15cm}{\footnotesize
21 rafts of data with proper headers and available with Butler.get~

\medskip }
\end{minipage} \\ \cdashline{2-2}

 & Expected Result \\
 & \begin{minipage}[t]{15cm}{\footnotesize
data can be viewed.

\medskip }
\end{minipage} \\ \cdashline{2-2}

 & Actual Result \\
 & \begin{minipage}[t]{15cm}{\footnotesize

\medskip }
\end{minipage} \\ \cdashline{2-2}

 & Status: \textbf{ Not Executed } \\ \hline

\end{longtable}


\input{appendix.tex}
\end{document}
